On The Difficulty of Computing Non-Commutative Signature Gröbner Bases

### 2022-07-18 article_issac.tex
Prise en compte des corrections dans la partie 7.
Prise en compte des corrections sur la partie 7, version 2.

For $f^{[\alpha]},g^{[\beta]},
h^{[\gamma]} \in I^{\Sigma},$
with $\alpha, g \neq 0,$
we say that 
$f^{[\alpha]}$ $\mathfrak{s}$-reduces to
$g^{[\beta]}$ by
$h^{[\gamma]}$
if there exist $a,b \in 
\left\langle X \right\rangle$
such that:
\begin{itemize}
\item $a \LM(h)b \in supp(f),$
\item $\mathfrak{s}(a \gamma b) \leq \mathfrak{s}(\alpha),$ and
\item $g^{[\beta]}=f^{[\alpha]}-\frac{coeff(f,a \LM(h)b}{\LC(g)} a h^{[\gamma]}b.$
\end{itemize}
Reduction by a set $G^{[\Sigma]} \in I^{[\Sigma]}$
is then defined as the 
reflexive, transitive closure
of the reduction by elements
of $G^{[\Sigma]} $.

@@

We then have the following fact:
\begin{itemize}
\item $s_1=\underline{xy \varepsilon_2}-\varepsilon_2 y^2+ x \varepsilon_1 y^2-y \varepsilon_1 y^2- \varepsilon_1 x y^2 \in Syz(f_1,f_2)$,
\item $s_2=\underline{xy \varepsilon_1}-yx\varepsilon_1 -  \varepsilon_1 x^2+y
  \varepsilon_1 xy \in Syz(f_1,f_2)$.
\fixmecc{j'ai l'impression que ce n'est pas une syzygie. On peut prendre à la
  place $s_2=\underline{xy\varepsilon_1}-\varepsilon_1yx+x\varepsilon_2-\varepsilon_2x$}  
\end{itemize}
In addition, the following are trivial syzygys:

\begin{itemize}
\item $s_3=\underline{x \varepsilon_1}-y\varepsilon_1- \varepsilon_1 x + \varepsilon_1 y \in Syz(f_1,f_2)$,
\item $s_4=\underline{y^2 \varepsilon_1}-\varepsilon_2 x +  \varepsilon_2 y \in Syz(f_1,f_2)$.
\item $s_5=\underline{x \varepsilon_2}-y\varepsilon_2- y^2 \varepsilon_2  \in
  Syz(f_1,f_2)$,
  \fixmecc{ce ne serait pas plutôt
    $\underline{x\varepsilon_2}-y\varepsilon_2-\varepsilon_1y^2$?} 
\item $s_6=\underline{y^2 \varepsilon_2}-\varepsilon_2 y^2 \in Syz(f_1,f_2)$.
\end{itemize}

We then state that:
\begin{lem}
The module of syzygys $Syz(f_1,f_2)$ admits $(s_1,\dots,s_6)$
as a Gröbner basis.
\end{lem}
\begin{proof}
Let $m=a \varepsilon_1 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$.
Then we distinguish the following cases.
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_3).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_2).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_4).$
\item If $a = y,$ then $s = y \varepsilon_1 u+  \varepsilon_1 v + \varepsilon_2 w$ for some polynomials $u,v,w.$
Applying $\overline{\cdot}$ (mapping $\varepsilon_i$ to $f_i$), we 
obtain that $y (x-y) u+  (x-y) v + y^2 w=0.$
On the left hand-side, the polynomial $xv$ contains all the monomials
with prefix $x$, which implies 
that no cancellation with other terms can occur,
and then $v=0.$
Similarly, $yxu$ contains all the monomials
with prefix $yx$, which then implies that
$u=0$ and then $y^2 w=0$ and $w=0$, and we get
a contradiction.
\item If $a = 1,$ then $s = \varepsilon_1 u+  \varepsilon_2 v $ for some polynomials $u,v.$
Again, applying $\overline{\cdot}$, we 
obtain that $u=v=0$ which is a contradiction.
\end{enumerate}
Similarly, let $m=a \varepsilon_2 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$. Then:
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_5).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_1).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_6).$
\item If $a = y,$ we obtain a contradiction \fixmecc{on peut avoir
  $\underline{y\varepsilon_2}-\varepsilon_2y$, mais c'est une syzygie principale}.
\item If $a = 1,$ we also obtain a contradiction.
\end{enumerate}

In conclusion, the leading monomials in $Syz(f_1,f_2)$
are of one of the following forms, for some $i=1,2$, $\alpha, \beta \in \left\langle x,y \right\rangle$:
\begin{itemize}
\item $\alpha x \varepsilon_i \beta,$
\item $\alpha xy \varepsilon_i \beta,$
\item $\alpha y^2 \varepsilon_i \beta,$
\end{itemize}
which are all divisible by some $\LM(s_j).$
This concludes the proof.
\end{proof}

@@

\section{Implementation}

>>>>

For $f^{[\alpha]},g^{[\beta]},
h^{[\gamma]} \in I^{\Sigma},$
with $\alpha, g \neq 0,$
we say that 
$f^{[\alpha]}$ $\mathfrak{s}$-reduces to
$g^{[\beta]}$ by
$h^{[\gamma]}$
if there exist $a,b \in 
\left\langle X \right\rangle$
such that:
\begin{itemize}
\item $a \LM(h)b \in supp(f),$
\item $\mathfrak{s}(a \gamma b) \leq \mathfrak{s}(\alpha),$ and
\item $g^{[\beta]}=f^{[\alpha]}-\frac{\text{coeff}(f,a \LM(h)b)}{\LC(g)} a h^{[\gamma]}b.$
\end{itemize}
Reduction by a set $G^{[\Sigma]} \subset I^{[\Sigma]}$
is then defined as the 
reflexive, transitive closure
of the reduction by elements
of $G^{[\Sigma]} $.

@@

We then have the following fact:
\begin{itemize}
%\item $s_1=\underline{xy \varepsilon_2}-\varepsilon_2 y^2+ x \varepsilon_1 y^2-y \varepsilon_1 y^2- \varepsilon_1 x y^2 \in Syz(f_1,f_2)$,
\item $s_1=\underline{xy\varepsilon_1}-\varepsilon_1yx+x\varepsilon_2-\varepsilon_2x \in Syz(f_1,f_2)$,
\item $s_2=\underline{y \varepsilon_2}-\varepsilon_2 y \in Syz(f_1,f_2)$. 
\end{itemize}
In addition, the following are trivial syzygys:

\begin{itemize}
\item $s_3=\underline{x \varepsilon_1}-y\varepsilon_1- \varepsilon_1 x + \varepsilon_1 y \in Syz(f_1,f_2)$,
\item $s_4=\underline{y^2 \varepsilon_1}-\varepsilon_2 x +  \varepsilon_2 y \in Syz(f_1,f_2)$,
\item $s_5=\underline{x\varepsilon_2}-y\varepsilon_2-\varepsilon_1y^2  \in
  Syz(f_1,f_2)$,
\end{itemize}

We then state that:
\begin{lem}
The module of syzygys $Syz(f_1,f_2)$ admits $(s_1,\dots,s_5)$
as a Gröbner basis.
\end{lem}
\begin{proof}
Let $m=a \varepsilon_1 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$.
Then we distinguish the following cases.
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_3).$
\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_1).$
\item If $a = \dots y^2$ then $m$ is divisible by $\LM(s_4).$
\item If $a = y,$ then $s = y \varepsilon_1 u+  \varepsilon_1 v + \varepsilon_2 w$ for some polynomials $u,v,w.$
Applying $\overline{\cdot}$ (mapping $\varepsilon_i$ to $f_i$), we 
obtain that $y (x-y) u+  (x-y) v + y^2 w=0.$
On the left-hand side, the polynomial $xv$ contains all the monomials
with prefix $x$, which implies 
that no cancellation with other terms can occur,
and then $v=0.$
Similarly, $yxu$ contains all the monomials
with prefix $yx$, which then implies that
$u=0$ and then $y^2 w=0$ and $w=0$, and we get
a contradiction.
\item If $a = 1,$ then $s = \varepsilon_1 u+  \varepsilon_2 v $ for some polynomials $u,v.$
Applying $\overline{\cdot}$, we 
obtain that $xu-yu+y^2v=0.$ On the left-hand side, 
the polynomial $xu$ contains all the monomials
with prefix $x$, which implies 
that no cancellation with other terms can occur,
and then $u=0,$ and consequently, $v=0$, which is a contradiction.
\end{enumerate}
Similarly, let $m=a \varepsilon_2 b \in \MM \left( \mathscr{F}_2 \right)$
be a leading monomial of a syzygy $s$. Then:
\begin{enumerate}
\item If $a = \dots x$ then $m$ is divisible by $\LM(s_5).$
%\item If $a = \dots xy$ then $m$ is divisible by $\LM(s_1).$
\item If $a = \dots y$ then $m$ is divisible by $\LM(s_2).$
\item If $a = 1,$ then $s = \varepsilon_1 u+  \varepsilon_2 v $ for some polynomials $u,v$ and 
we get the same contradiction as for $m=\varepsilon_1b.$ 
\end{enumerate}

In conclusion, the leading monomials in $Syz(f_1,f_2)$
are of one of the following forms, for some $i=1,2$, $\alpha, \beta \in \left\langle x,y \right\rangle$:
\begin{itemize}
\item $\alpha x \varepsilon_i \beta,$
\item $\alpha xy \varepsilon_i \beta,$
\item $\alpha y^2 \varepsilon_1 \beta,$
\item $\alpha y \varepsilon_2 \beta,$
\end{itemize}
which are all divisible by some $\LM(s_j).$
This concludes the proof.
\end{proof}

@@

\section{Implementation?}
